---
title: "Util_Global.R"
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "##", fig.retina = 2, fig.path = "README_figs/README-")
```
![GitHub top language](https://img.shields.io/github/languages/top/shringi/util_Global)
![GitHub code size in bytes](https://img.shields.io/github/languages/code-size/shringi/util_Global)
![GitHub](https://img.shields.io/github/license/shringi/util_Global)

![GitHub commit activity](https://img.shields.io/github/commit-activity/y/shringi/util_Global)
![GitHub last commit](https://img.shields.io/github/last-commit/shringi/util_Global)

![GitHub issues](https://img.shields.io/github/issues/shringi/util_Global)



# Motivation
R and its package repository are great. I could find almost all kinds of functions, various tricks and tips online. However, as I worked on R  and R studio long enough. I happen to create custom functions which I find it convenient to use for my purpose. I slowly began to realize that I should share some of them with others in case they find it helpful.

# Functions
The following functions are implemented (broad category wise)

### Calculations
- `interpolate`
- `max.adv`
- `min.adv`
- `sum.adv`
- `mov.avg`
- `mov.sd`
- `rm.na`

### Graphics
### Info
### Management
### Manipulation
### Operators
### Print
### Productivity
### Summary



# Installation
Just download the **util_Global.R** file. 
```{r}
source("util_Global.R")
install("tidyverse")

```
Source it locally and you are good to go.


# Usage


### drop_cols() : Select out columns based on values
#### syntax
```psudeocode
drop_cols(data, ..., contains = "", na.rm = TRUE)
```
#### Usage
```{r}
df_c <- data.frame(c1 = c(1,2,3,4),
                   c2 = c(11, 12, 13, NA),
                   c3 = c("a", "a", "a", "a"),
                   c4 = c("a", "a", "a", NA_character_),
                   c5 = rep(NA_character_, 4),
                   c6 = rep("",4),
                   c7 = c(rep(10,3),NA))

# Filterning blank or NA filled columns
df_c %>% drop_cols()

# Filterning blank or NA filled columns from a range
df_c %>% drop_cols(c4:c6)

# Filtering blacnk or NA fillder columns
df_c %>% drop_cols(c4:c6, contains = list("a", 10))
```
### install() : loading packages
every now or then you require a package to run before you can use some R code you found online. Its typically starts with loading a `library()` or `require()`. For example

If "package_name" is already install then you are good to go, however if it is not installed (which is the case sometimes), then you will get an error as following-

```pseudocode
Error in library("package_name") : 
  there is no package called ‘package_name’
```

 Then one needs install it manually either by using RStudio GUI or writing a command such as 

```R
install.packages("package_name")
```

I thought, wouldn't it be better that I write one command `install("package_name")` and it detects automatically whether the package is available or not. If it not available then goes ahead and downloads it automatically behind the scenes using `install.packages()`, else loads it using `library()` command. So created one such command `install()` for my personal use and many others such tiny tweaked functions and thought of sharing on the github.

# Scripts

## **util_Global.R**

This is the main scripts which hosts all the custom functions. A list of function and their usage are mentioned below.

## util_Global_Archived.R

All the functions, which I no longer use, or found a way around are shifted here.

## Snippets.txt

A file containing plain snippets. Copy these snippets, modify and add in your RStudio settings (Tools > Global Options > Code > Editing > Snippets > Edit Snippets button) for handy use. You can find more information about RStudio Snippets from [here](https://support.rstudio.com/hc/en-us/articles/204463668-Code-Snippets).

# Feedback

- Please feel free to raise a issue on github if you are find a bug or suggest a feature.
- If you come across any  functions which surpasses any of the functions or then please let me know in the issues as well.
